### 2022-06-06 main/chapter_2ljets.tex
add summary tables from unblinding and no_sr

Figure~\ref{fig:2ljets_prepre}

@@

@@

>>>>

Figure~\ref{fig:2ljets_prepre}
Figure~\ref{fig:2ljets_summary_unblinding}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_unblinding_log.png}
\caption[
First unblinded summary table from 28th September 2020
]{%
First unblinded summary table from 28th September 2020.
Backgrounds are fitted to data in control and signal regions.
Errors include all variations that were evaluated at the time.
Data and backgrounds were later reproduced with updated software and tighter
lepton definitions, leading to a general reduction in yields.
}
\label{fig:2ljets_summary_unblinding}
\end{figure}

@@

Figure~\ref{fig:2ljets_summary_no_sr}

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figures/2ljets_summary_no_sr_log.pdf}
\caption[
Alternative summary table with backgrounds fitted to control regions only
]{%
Alternative summary table with backgrounds fitted to control regions only.
A version fitted also to signal regions is shown in
Figure~\ref{fig:2ljets_summary}.
Fitting to signal regions is policy of the \atlas\ SUSY group, but deviates
from the intentions of the significance measure.
Because the post-fit yields in SR-Low achieve a small negative significance,
all mentions of its deficit were removed from the paper.
}
\label{fig:2ljets_summary_no_sr}
\end{figure}
